---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lubridate))
source("~/Dropbox/Documents/Github_mining/src/R/project_info.R")
repo_data_main <- load_repo_features(saved_repo_features_main)
repo_data_high_prof <- load_repo_features(saved_repo_features_high_prof)
repo_data_all <- load_repo_features_all()
```

### Amount of code and type system

High profile repos contain more code and a higher percentage of it is statically typed.

```{r type_system}
ggplot(repo_data_all %>% 
         filter(total_bytes_no_data_type_system_static > 0 & total_bytes_no_data_type_system_static > 0), 
       aes(y = log10(total_bytes_no_data_type_system_static), 
           x = log10(total_file_size_no_data),
           col = is_high_profile)) +
  geom_point(size = 1) +
  geom_point(data = subset(repo_data_all, is_high_profile), size = 1) +
  ylab("Total bytes of statically typed code (log10)") +
  xlab("Total bytes of code (log10)") +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  xlim(0, 8) +
  ylim(0, 8)
```

### Team size and outside committers

High profile repos have more developers and more outside developers.

```{r committers}
plt_data_committers <- repo_data_all %>% 
  select(num_non_committing_authors, commit_authors, is_high_profile) %>%
  group_by(num_non_committing_authors, commit_authors, is_high_profile) %>%
  dplyr::summarize(Num_repos = n())
ggplot(plt_data_committers, 
       aes(y = num_non_committing_authors, 
           x = commit_authors,
           col = is_high_profile)) +
  geom_point(aes(size = Num_repos)) +
  geom_point(data = subset(plt_data_committers, is_high_profile), aes(size = Num_repos)) +
  ylab("Number of non-committing commit authors") +
  xlab("Number of commit authors") +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  #xlim(0, max(log10(repo_data_all$commit_authors), na.rm = T)) +
  ylim(0, max(repo_data_all$num_non_committing_authors, na.rm = T)) +
  scale_x_log10() +
  stat_function(fun = function(x) {x}, geom="line", color = "black")
```

### Number of files and file size

High profile repos have more source files but similar file sizes

```{r num_files_file_size}
plt_data_num_files <- repo_data_all %>% filter(num_files_no_data > 0 & mean_lines_code_no_data > 0)
breaks <- c(1, 10, 100, 1000, 10000)
ggplot(plt_data_num_files, 
       aes(x = num_files_no_data, 
           y = mean_lines_code_no_data,
           col = is_high_profile)) +
  geom_point(size = 1) +
  geom_point(data = subset(plt_data_num_files, is_high_profile), size = 1) +
  xlab("Total source files") +
  ylab("Mean lines of code per source file") +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  scale_x_log10(breaks = breaks) +
  scale_y_log10(breaks = breaks)
```

### Topics

Some paper topics are associated with higher community engagement, repo size, and commit activity

```{r topics, fig.width = 8, fig.height = 8}
as.tbl(repo_data_main) %>% 
  select(commits, commit_authors, forks_count, subscribers_count, 
         watchers_count, num_citations_per_week_pmc_minus_2_years, 
         total_file_size_no_data, num_files_no_data, contains("topic")) %>% 
  melt(id.vars = c("commits", "commit_authors", "forks_count", 
                   "subscribers_count", "watchers_count", "num_citations_per_week_pmc_minus_2_years",
                   "total_file_size_no_data", "num_files_no_data")) %>% 
  filter(value) %>% 
  as.tbl() %>% 
  select(-value) %>% 
  dplyr::rename(Topic = variable) %>% 
  group_by(Topic) %>%
  dplyr::summarize(
    `Mean commits` = mean(commits, na.rm = T),
    `Mean commit authors` = mean(commit_authors, na.rm = T),
    `Mean forks` = mean(forks_count, na.rm = T),
    `Mean subscribers` = mean(subscribers_count, na.rm = T),
    `Mean watchers` = mean(watchers_count, na.rm = T),
    `Mean PMC citations / week` = mean(num_citations_per_week_pmc_minus_2_years, na.rm = T),
    `Mean megabytes of code` = mean(total_file_size_no_data, na.rm = T) / 1000000,
    `Mean number of files` = mean(num_files_no_data, na.rm = T)
  ) %>%
  melt(id.vars = "Topic") %>%
  mutate(Topic = gsub("topic_", "", Topic)) %>%
  mutate(Topic = gsub("_", " ", Topic)) %>%
  mutate(Topic = gsub("RNA.seq", "RNA-seq", Topic)) %>%
  ggplot(aes(x = variable, y = value, fill = factor(Topic))) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  guides(fill = guide_legend(title="Abstract includes topic")) +
  theme(legend.text = element_text(size=10),
        legend.title = element_text(size = 11),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        strip.text = element_text(size = 10)) +
  scale_fill_brewer(palette="Dark2") +
  facet_wrap(~variable, scales = "free", ncol = 2)
```

### Commits after publication

Committing to the repo after publication is associated with more community engagement, more development activity, and more citations.

```{r commits_after_publication, fig.width = 9, fig.height = 7}
plt_data_commits_after_pub <- as.tbl(repo_data_main) %>% 
  select(commits, commit_authors, forks_count, subscribers_count, 
         watchers_count, num_citations_per_week_pmc_minus_2_years, 
         mean_commit_message_len, pct_commits_diff_author_committer, 
         num_non_committing_authors, commits_after_article_in_pubmed) %>% 
  filter(!is.na(commits_after_article_in_pubmed)) %>%
  dplyr::rename(
    `Total commits` = commits,
    `Commit authors` = commit_authors, 
    `Total forks` = forks_count, 
    `Total subscribers` = subscribers_count, 
    `Total watchers` = watchers_count,
    `PMC citations / week` = num_citations_per_week_pmc_minus_2_years,
    `Commit message len` = mean_commit_message_len,
    `Pct outside commits` = pct_commits_diff_author_committer,
    `Outside cmt authors` = num_non_committing_authors,
    `Commits after\npublication` = commits_after_article_in_pubmed
  ) %>% 
  melt(id.vars = "Commits after\npublication")

# Get smallest positive value of each variable so we can take logs
min_pos <- plt_data_commits_after_pub %>% 
  filter(value > 0) %>%
  group_by(variable) %>%
  summarize(min_pos = min(value))

# Remove top outliers for plot
p_outlier <- 1 # 1 means no filtering for outliers
outlier_cutoff <- plt_data_commits_after_pub %>%
  group_by(variable) %>%
  summarize(outlier_cutoff = quantile(value, probs = p_outlier, na.rm = T))

plt_data_commits_after_pub <- plt_data_commits_after_pub %>% 
  left_join(min_pos, by = "variable") %>%
  left_join(outlier_cutoff, by = "variable")

# Replace 0's and NA's by minimum positive value
plt_data_commits_after_pub$value_pos <- apply(plt_data_commits_after_pub, 1, function(row) {
  val <- as.numeric(row["value"])
  mp <- as.numeric(row["min_pos"])
  if(is.na(val)) mp
  else max(val, mp)
})

plt_data_commits_after_pub <- plt_data_commits_after_pub %>%
  filter(value_pos <= outlier_cutoff) %>%
  select(`Commits after\npublication`, variable, value_pos)

ggplot(plt_data_commits_after_pub, aes(variable, value_pos)) +
  geom_boxplot(aes(fill = `Commits after\npublication`)) +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  scale_y_log10() +
  theme_bw() +
  theme(legend.text = element_text(size=10),
        legend.title = element_text(size = 11),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        strip.text = element_text(size = 10))
```

### Outside contributors

```{r outside_contributors, fig.width = 9, fig.height = 3}
plt_data_outside_contrib <- as.tbl(repo_data_all) %>% 
  select(forks_count, subscribers_count, watchers_count, num_non_committing_authors, is_high_profile) %>% 
  mutate(forks_count = forks_count + 1,
         subscribers_count = subscribers_count + 1,
         watchers_count = watchers_count + 1,
         num_non_committing_authors = num_non_committing_authors + 1) %>%
  dplyr::rename(
    `Total forks + 1` = forks_count, 
    `Total subscribers + 1` = subscribers_count, 
    `Total watchers + 1` = watchers_count,
    `Outside commit authors + 1` = num_non_committing_authors
  ) %>%
  melt(id.vars = c("Outside commit authors + 1", "is_high_profile")) %>%
  group_by(`Outside commit authors + 1`, is_high_profile, variable, value) %>%
  summarize(`Num repos` = n())

ggplot(plt_data_outside_contrib) +
  geom_point(aes(size = `Num repos`, 
                 x = `Outside commit authors + 1`, 
                 y = value, col = is_high_profile)) +
  geom_point(data = subset(plt_data_outside_contrib, is_high_profile),
             aes(size = `Num repos`, 
                 x = `Outside commit authors + 1`, 
                 y = value, col = is_high_profile)) +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        strip.text = element_text(size = 11)) +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  scale_y_log10(breaks = c(1, 10, 100, 1000, 10000)) +
  scale_x_log10()

```

### Commit authors and community

```{r commit_authors, fig.width = 9, fig.height = 3}
plt_data_commit_authors <- as.tbl(repo_data_all) %>% 
  select(forks_count, subscribers_count, watchers_count, commit_authors, is_high_profile) %>% 
  mutate(forks_count = forks_count + 1,
         subscribers_count = subscribers_count + 1,
         watchers_count = watchers_count + 1) %>%
  dplyr::rename(
    `Total forks + 1` = forks_count, 
    `Total subscribers + 1` = subscribers_count, 
    `Total watchers + 1` = watchers_count,
    `Commit authors` = commit_authors,
    `High profile` = is_high_profile
  ) %>%
  group_by(`Total forks + 1`, `Total subscribers + 1`, `Total watchers + 1`, `Commit authors`, `High profile`) %>%
  summarize(`Num repos` = n()) %>%
  melt(id.vars = c("Commit authors", "High profile", "Num repos"))

ggplot(plt_data_commit_authors) +
  geom_point(aes(x = `Commit authors`, 
                 y = value,
                 col = `High profile`,
                 size = `Num repos`)) +
  geom_point(data = subset(plt_data_commit_authors, `High profile`),
             aes(x = `Commit authors`, 
                 y = value,
                 col = `High profile`,
                 size = `Num repos`)) +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title.y = element_blank(),
        strip.text = element_text(size = 11)) +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  scale_y_log10(breaks = c(1, 10, 100, 1000)) +
  scale_x_log10()
```

### Commits

```{r commits, fig.width = 10, fig.height = 6}
plt_data_commit_authors <- as.tbl(repo_data_all) %>% 
  select(commits, mean_commits_per_month, consecutive_months_with_commits, 
         commit_span_days, mean_files_added_per_month, num_days_new_files_added,
         consecutive_months_no_commits, is_high_profile) %>% 
  mutate(consecutive_months_no_commits = consecutive_months_no_commits + 1) %>%
  dplyr::rename(
    `Total commits` = commits,
    `Mean commits/month` = mean_commits_per_month,
    `Max cons. months with commits` = consecutive_months_with_commits,
    `Project duration (days)` = commit_span_days,
    `Mean new files per month` = mean_files_added_per_month,
    `Days with new files added` = num_days_new_files_added,
    `1 + max cons. months no commits` = consecutive_months_no_commits,
    `High profile` = is_high_profile
  ) %>%
  group_by(`Total commits`, `Mean commits/month`, `Max cons. months with commits`, 
           `Project duration (days)`, `Mean new files per month`, 
           `Days with new files added`, `1 + max cons. months no commits`, `High profile`) %>%
  summarize(`Num repos` = n()) %>%
  melt(id.vars = c("Total commits", "High profile", "Num repos"))

ggplot(plt_data_commit_authors) +
  geom_point(aes(x = `Total commits`, 
                 y = value,
                 col = `High profile`,
                 size = `Num repos`)) +
  geom_point(data = subset(plt_data_commit_authors, `High profile`), 
             aes(x = `Total commits`, 
                 y = value,
                 col = `High profile`,
                 size = `Num repos`)) +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title.y = element_blank(),
        strip.text = element_text(size = 10)) +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  scale_y_log10(breaks = c(1, 10, 100, 1000)) +
  scale_x_log10(breaks = c(1, 10, 100, 1000, 10000))
```

### Languages: file sizes and lines of code

```{r langs, fig.height = 6, fig.width = 12}
top_langs <- sapply(top_langs, format_lang_as_header)
lang_cols <- unname(c(sapply(top_langs, function(x) paste("num_files_", x, sep = "")), sapply(top_langs, function(x) paste("mean_lines_code_", x, sep = ""))))
plt_data_langs <- data.frame(`Number of files` = integer(), 
                             `Mean lines of code per file` = numeric(), 
                             is_high_profile = logical(), 
                             lang = character())
for(lang in top_langs) {
  col_nf <- paste("num_files_", lang, sep = "")
  col_loc <- paste("mean_lines_code_", lang, sep = "")
  plt_data_langs <- rbind(plt_data_langs,
                          repo_data_all %>% 
                            select(!!as.name(col_nf), !!as.name(col_loc), is_high_profile) %>% 
                            mutate(lang = lang) %>% 
                            rename(`Number of files` = !!as.name(col_nf), 
                                   `Mean lines of code per file` = !!as.name(col_loc)) %>% 
                            filter(`Number of files` > 0 & `Mean lines of code per file` > 0))
}

ggplot(plt_data_langs) +
  geom_point(aes(x = `Number of files`, 
                 y = `Mean lines of code per file`,
                 col = is_high_profile)) +
  geom_point(data = subset(plt_data_langs, is_high_profile), 
             aes(x = `Number of files`, 
                 y = `Mean lines of code per file`,
                 col = is_high_profile)) +
  scale_color_manual(values=c(color_main, color_high_prof), labels = c("Main repos", "High profile repos")) +
  theme_bw() +
  guides(color = guide_legend(title = "Dataset")) +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  facet_wrap(~lang, scales = "free", ncol = 5) +
  scale_y_log10(breaks = c(1, 10, 100, 1000, 10000)) +
  scale_x_log10(breaks = c(1, 10, 100, 1000, 10000))
```

### Years by topic

```{r years_by_topic, fig.height = 11, fig.width = 8}
plt_data_years_by_topic <- repo_data_main %>%
  select(first_commit, date_pubmed, contains("topic")) %>%
  mutate(year_first_commit = year(first_commit),
         year_pubmed = year(date_pubmed)) %>%
  select(-first_commit, -date_pubmed) %>%
  melt(id.vars = c("year_first_commit", "year_pubmed")) %>%
  filter(value) %>%
  group_by(year_first_commit, year_pubmed, variable) %>%
  summarize(num_repos = n()) %>%
  filter(!is.na(year_first_commit) & !is.na(year_pubmed)) %>%
  rename(Topic = variable)

plt_data_years_by_topic$Topic <- sapply(plt_data_years_by_topic$Topic, function(x) {
  gsub("_", " ", gsub("topic_", "", gsub("RNA.seq", "RNA-seq", x)))
})

min_year <- min(c(plt_data_years_by_topic$year_first_commit, plt_data_years_by_topic$year_pubmed))
max_year <- max(c(plt_data_years_by_topic$year_first_commit, plt_data_years_by_topic$year_pubmed))
ggplot(plt_data_years_by_topic) +
  geom_point(aes(x = year_first_commit, 
                 y = year_pubmed,
                 size = num_repos)) +
  theme_bw() +
  theme(legend.text = element_text(size=12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        strip.text = element_text(size = 10)) +
  facet_wrap(~Topic, scales = "fixed", ncol = 2) +
  xlim(min_year, max_year) +
  ylim(min_year, max_year)

```

### Session info

```{r session_info}
sessionInfo()
```