---
title: 'Exploratory analysis'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r echo = F}
rm(list=ls())
suppressPackageStartupMessages(library(bigrquery))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
setwd("~/Documents/Github_mining/src/R/exploratory_analysis")
```

# Project info

```{r cache = T}
proj <- "github-bioinformatics-157418"
ds_gh <- "test_repos"
ds_analysis <- "test_repos_analysis_results"
```

# Programming languages

### Load the data from BigQuery

```{r cache = T, fig.height = 7, fig.width = 8}
repos_by_lang <- list_tabledata(project = proj, dataset = ds_analysis, table = "num_repos_by_language")
repos_by_lang <- arrange(repos_by_lang, desc(num_repos))
lang_by_repo <- list_tabledata(project = proj, dataset = ds_analysis, table = "language_list_by_repo")
lang_bytes <- list_tabledata(project = proj, dataset = ds_analysis, table = "bytes_by_language")
```

### Number of repos by language

```{r}
# Get the top languages
top_langs <- arrange(repos_by_lang[1:30,], num_repos)
top_langs$language_name <- factor(top_langs$language_name, levels = top_langs$language_name)

# Plot number of repos by language
ggplot(top_langs, aes(x = factor(language_name), y = num_repos)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(y = paste("Number of repos including language (n = ", nrow(lang_by_repo), ")", sep = ""),
       x = "Language",
       title = "Number of repos by language") +
  theme(plot.title = element_text(size = 24),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

### Number of repos by language pair

```{r}
# Identify languages
lang <- sort(lang_bytes$language_name)
nlang <- length(lang)
npair <- nlang * (nlang - 1) / 2

mkPair <- function(l1, l2) {
  paste(l1, l2, sep=", ")
}

# Make list of all possible language pairs
all_pairs <- apply(expand.grid(lang, lang), 1, function(x) {
      l1 <- as.character(x[1])
      l2 <- as.character(x[2])
      if(l1 < l2) {
        mkPair(l1, l2)
      }
      else NA
})
all_pairs <- all_pairs[which(!is.na(all_pairs))]

# Empty data frame of pair counts
pair_count <- data.frame(num_repos = matrix(0, nrow = npair, ncol = 1), 
                         row.names = all_pairs)

# Function to update pair counts based on language list for one repo
update_pair_count <- function(cslist) {
  l <- unlist(strsplit(cslist, ',', fixed = T))
  l <- l[which(!is.na(l))]
  apply(expand.grid(l, l), 1, function(x) {
    l1 <- as.character(x[1])
    l2 <- as.character(x[2])
    if(l1 < l2) {
      pair_count[mkPair(l1, l2), 1] <<- pair_count[mkPair(l1, l2), 1] + 1
    }
  })
}

# Update the pair counts for all repos
x <- lapply(lang_by_repo$languages, update_pair_count)
rm(x)

# Sort pairs by number of repos
pair_count$languages <- row.names(pair_count)
pair_count <- arrange(pair_count, desc(num_repos))

# Get the top pairs
top_pairs <- pair_count[1:30,]
top_pairs <- arrange(top_pairs, num_repos)
top_pairs$languages <- factor(top_pairs$languages, levels = top_pairs$languages)

# Plot number of repos by language pair
ggplot(top_pairs, aes(x = languages, y = num_repos)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(y = paste("Number of repos including both languages (n = ", nrow(lang_by_repo), ")", sep = ""),
       x = "Languages",
       title = "Number of repos by language pair") +
  theme(plot.title = element_text(size = 24),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

### Total size of source files by language

Use BigQuery's built-in "languages" table, not our CLOC results

```{r}
# Construct a vector of number of bytes per language
language <- lang_bytes$language_name
bytes <- lang_bytes$total_bytes
names(bytes) <- language
bytes <- bytes[order(-bytes)]

# Get the top languages
num_top_languages <- 25
top_languages <- bytes[1:num_top_languages]
names(top_languages) <- names(bytes)[1:num_top_languages]
top_languages <- top_languages[order(top_languages)]
# All other languages
others <- sum(bytes[1+num_top_languages:length(bytes)], na.rm=T)
new_names <- c("All others", names(top_languages))
top_languages <- c(others, top_languages)
names(top_languages) <- new_names

# Plot bytes per language
par(mar=c(5,12,4,2))
barplot(
  t(as.matrix(top_languages)),
  horiz = T,
  col = "darkorchid4",
  las=1,
  main="Total size of source files",
  axes=F
)
axis(1, at=c(0, 100000000, 200000000, 300000000), labels=c("0", "100Mb", "200Mb", "300Mb"))
```

# Join all repo-level data

```{r cache = T, fig.height = 7, fig.width = 8}
# Load all the repo-level data from BigQuery and do a full join by repo name
table_list <- c("language_list_by_repo", "num_languages_by_repo", "lines_of_code_by_repo", 
                "project_duration_by_repo", "num_forks_by_repo", "num_watchers_by_repo", 
                "num_actors_by_repo", "num_devs_by_repo", "commit_types_by_repo", "test_cases_by_repo")
repo_level_data <- data.frame(repo_name = character())
for(table in table_list) {
  table_data <- list_tabledata(project = proj, dataset = ds_analysis, table = table)
  repo_level_data <- full_join(repo_level_data, table_data, by = "repo_name")
}
```

# Project duration

### Histogram of project duration

```{r}
qplot(repo_level_data$commit_span_days,
      geom = "histogram",
      binwidth = 100,
      main = "Histogram of project duration",
      xlab = "Time from first commit to latest commit (years)",
      ylab = "Number of repos",
      fill = I("darkmagenta")) +
  theme(plot.title = element_text(size = 24),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16)) +
  scale_x_continuous(breaks = function(x) {seq(0, x[2], by=365)},
                     labels = function(x) x / 365)
```


### Scatter plot of latest commit vs first commit

```{r}
min_date <- min(repo_level_data$first_commit, na.rm = T)
max_date <- max(repo_level_data$last_commit, na.rm = T)
ggplot(data = repo_level_data, aes(x = first_commit, y = last_commit)) +
  geom_point(aes(color = commit_span_days)) +
  scale_color_gradientn(colors = c("red", "green", "blue"), 
                        name = "Commit span (years)",
                        labels = function(x) round(x / 365)) +
  coord_cartesian(xlim = c(min_date, max_date),
                  ylim = c(min_date, max_date)) +
  labs(title = "Project time spans",
       x = "First commit",
       y = "Latest commit") +
  theme(plot.title = element_text(size = 24),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

# Bug fix commits

### Relationship with project duration

```{r}
commits_filtered <- repo_level_data %>%
  filter(num_commits > 100) %>%
  mutate(pct_bug_fix = num_bug_fix_commits / num_commits)
summary(lm(pct_bug_fix ~ commit_span_days, data = commits_filtered))
ggplot(commits_filtered, aes(x = commit_span_days, y = pct_bug_fix)) +
  geom_point() +
  geom_smooth(method = lm) + 
  scale_x_continuous(breaks = function(x) {seq(0, x[2], by=365)},
                     labels = function(x) x / 365) +
  labs(x = "Time from first commit to last commit (years)",
       y = "Percentage of bug fix commits") +
  theme(axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))

```













