---
title: "Gender analysis of developers and paper authors"
output: html_document
---

## Environment setup

```{r setup}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(bigrquery))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(RColorBrewer))
source("~/Dropbox/Documents/Github_mining/src/R/project_info.R")
proj_main <- proj_main
proj_high_prof <- proj_high_profile
```

## Load data from BigQuery

Genders were inferred for each "valid" unique name of paper authors, commit authors and committers.

```{r load_names}
# Get mapping of names to genders from BigQuery
gender_main <- list_tabledata(project = proj_main, dataset = ds_analysis, table = table_gender_by_name)
gender_high_prof <- list_tabledata(project = proj_high_prof, dataset = ds_analysis, table = table_gender_by_name)

# Look at gender breakdown of names we tried to call a gender on
gender_main %>% group_by(gender) %>% dplyr::summarize(num_developers = n())
gender_high_prof %>% group_by(gender) %>% dplyr::summarize(num_developers = n())

# Function to get gender for a first name
get_gender <- function(first_name, gender_table) {
  row <- which(gender_table$first_name == first_name)
  if(length(row) == 0) NA
  else gender_table[row[1], "gender"]
}

# Function to get gender for a full name
get_gender_full_name <- function(full_name, gender_table) {
  tokens <- unlist(strsplit(full_name, "\\s+"))
  get_gender(tokens[1], gender_table)
}
```

Get commit records

```{r load_commits}
# Function to load commits and do some processing
get_commits <- function(proj, gender_table) {
  query <- paste("
                  SELECT
                    repo_name,
                    author_login,
                    author_id,
                    author_name,
                    committer_login,
                    committer_id,
                    committer_name,
                    commit_message
                  FROM
                    [", proj, ":", ds_gh, ".", table_commits, "]
", sep = "")
  commits <- query_exec(query, project = proj, max_pages = Inf)
  commits <- commits %>% 
    left_join(gender_table %>% select(full_name, gender), by = c("author_name" = "full_name")) %>% 
    rename(author_gender = gender)  %>% 
    left_join(gender_table %>% select(full_name, gender), by = c("committer_name" = "full_name")) %>% 
    rename(committer_gender = gender)
  
  # Make a version of commits table with null author and committer logins filled in with author-specific info so they can be collapsed
  # Name fields are never null
  commits_no_null_login <- commits
  null_author_login <- which(is.na(commits_no_null_login$author_login))
  null_committer_login <- which(is.na(commits_no_null_login$committer_login))
  commits_no_null_login[null_author_login, "author_login"] <- commits_no_null_login[null_author_login, "author_name"]
  commits_no_null_login[null_committer_login, "committer_login"] <- commits_no_null_login[null_committer_login, "committer_name"]
  
  # Return an object
  list(commits = commits, commits_no_null_login = commits_no_null_login)
}

# Get commit info for main and high profile repos
commit_info_main <- get_commits(proj_main, gender_main)
commit_info_high_prof <- get_commits(proj_high_prof, gender_high_prof)
```

Get paper author lists

```{r load_author_lists}
# Function to get author lists of papers from BigQuery
get_author_lists <- function(proj) {
  query <- paste("SELECT repo_name, title, authors FROM [", 
                 proj, ":", ds_lit_search, ".", table_article_metadata, "]",
                 sep = "")
  query_exec(query, project = proj, max_pages = Inf)
}

# Get author lists
author_lists_main <- get_author_lists(proj_main)
author_lists_high_prof <- get_author_lists(proj_high_prof)
```

## Combine commit authors and committers into one table and look at gender breakdown

```{r developers}
# Collapse by name and login, keeping a version with a gender call where possible
commit_authors <- function(commits_no_null_login) {
  commits_no_null_login %>% 
    select(author_login, author_name, author_gender) %>% 
    group_by(author_name) %>% 
    arrange(author_gender) %>% 
    filter(row_number() == 1) %>% 
    ungroup() %>% 
    group_by(author_login) %>% 
    arrange(author_gender) %>% 
    filter(row_number() == 1) %>%
    rename(name = author_name, gender = author_gender) %>%
    ungroup() %>%
    select(name, gender)
}
committers <- function(commits_no_null_login) {
  commits_no_null_login %>% 
    select(committer_login, committer_name, committer_gender) %>% 
    group_by(committer_name) %>% 
    arrange(committer_gender) %>% 
    filter(row_number() == 1) %>% 
    ungroup() %>% 
    group_by(committer_login) %>% 
    arrange(committer_gender) %>% 
    filter(row_number() == 1) %>%
    rename(name = committer_name, gender = committer_gender) %>%
    ungroup() %>%
    select(name, gender)
}
developers <- function(commit_authors, committers) {
  rbind(commit_authors, committers) %>% unique() %>% arrange(name)
}

# Get commit authors and committers for main repos and high profile
commit_authors_main <- commit_authors(commit_info_main$commits_no_null_login)
commit_authors_high_prof <- commit_authors(commit_info_high_prof$commits_no_null_login)
committers_main <- committers(commit_info_main$commits_no_null_login)
committers_high_prof <- committers(commit_info_high_prof$commits_no_null_login)
developers_main <- developers(commit_authors_main, committers_main)
developers_high_prof <- developers(commit_authors_high_prof, committers_high_prof)

# Look at gender breakdown of developers
developers_main %>% group_by(gender) %>% dplyr::summarize(num_developers = n())
developers_high_prof %>% group_by(gender) %>% dplyr::summarize(num_developers = n())
```

## Make table of paper authors and look at gender breakdown

```{r paper_authors}
# Function to get table of paper authors and genders
paper_authors <- function(author_lists, gender_table) {
  paper_author_full_names <- NULL
  for(author_list in author_lists$authors) {
    paper_author_full_names <- c(paper_author_full_names, 
                                 sapply(author_list, function(x) trimws(unlist(strsplit(x, ";")))))
  }
  paper_author_full_names <- unique(paper_author_full_names)
  paper_author_gender <- sapply(paper_author_full_names, function(x) get_gender_full_name(x, gender_table))
  data.frame(name = paper_author_full_names, gender = paper_author_gender)
}

# Get paper authors
paper_authors_main <- paper_authors(author_lists_main, gender_main)
paper_authors_high_prof <- paper_authors(author_lists_high_prof, gender_high_prof)

# Look at total number of unique names among commit authors, committers, paper authors
# Main repos
length(unique(c(commit_info_main$commits$author_name, commit_info_main$commits$committer_name, paper_authors_main$name)))
# High profile repos
length(unique(c(commit_info_high_prof$commits$author_name, 
                commit_info_high_prof$commits$committer_name, paper_authors_high_prof$name)))

# Look at gender breakdown of paper authors
paper_authors_main %>% group_by(gender) %>% dplyr::summarize(num_authors = n())
paper_authors_high_prof %>% group_by(gender) %>% dplyr::summarize(num_authors = n())
```

## Gender breakdown of commit authors and committers by repo

```{r summaries}
# Function to summarize commit authors by repo
commit_author_summary <- function(commits_no_null_login) {
  commits_no_null_login %>% 
    select(repo_name, author_login, author_name, author_gender) %>% 
    group_by(repo_name, author_name) %>% 
    arrange(author_gender) %>% 
    filter(row_number() == 1) %>% 
    ungroup() %>% 
    group_by(repo_name, author_login) %>% 
    arrange(author_gender) %>% 
    filter(row_number() == 1) %>%
    ungroup() %>%
    select(repo_name, author_name, author_gender) %>% 
    unique() %>% 
    group_by(repo_name, author_gender) %>% 
    dplyr::summarize(unique_author_names = n()) %>% 
    spread(author_gender, unique_author_names, fill = 0) %>%
    rename(no_gender = "<NA>") %>%
    ungroup() %>%
    data.frame()
}

# Function to summarize commits by repo
commit_summary <- function(commits_no_null_login) {
  commits_no_null_login %>% 
    select(repo_name, author_gender) %>% 
    group_by(repo_name, author_gender) %>% 
    dplyr::summarize(num_commits = n()) %>% 
    spread(author_gender, num_commits, fill = 0) %>% 
    rename(no_gender = "<NA>") %>% 
    ungroup %>% 
    data.frame()
}

# Summarize commit authors and commits by repo
commit_author_summary_main <- commit_author_summary(commit_info_main$commits_no_null_login)
commit_author_summary_high_prof <- commit_author_summary(commit_info_high_prof$commits_no_null_login)
commit_summary_main <- commit_summary(commit_info_main$commits_no_null_login)
commit_summary_high_prof <- commit_summary(commit_info_high_prof$commits_no_null_login)
```

## Functions to classify team types and calculate Shannon index of diversity

```{r diversity_functions}
# Max proportion of no gender calls to analyze a repo
max_no_gender <- 0.25

# Classify the repo by its gender breakdown
classify <- function(male, female, na) {
  total <- male + female + na
  if(na / total > max_no_gender) NA
  else {
    if (total == 1) {
      if (male == 1) "Solo male"
      else if(female == 1) "Solo female"
      else NA
    } else {
      if (male == 0) "All female"
      else if (female == 0) "All male"
      else if (male > female) "Majority male"
      else if (female > male) "Majority female"
      else "Equal"
    }
  }
}

# Shannon index of diversity
# counts is vector of category counts
shannon <- function(counts) {
  counts <- counts[which(counts != 0)]
  if(length(counts) == 0) 0
  else {
    proportions <- counts / sum(counts)
    -1 * sum(sapply(proportions, function(x) {x * log(x)}))
  }
}
```

## Calculate Shannon index and classify repos by commit authors

```{r diversity}
# Add Shannon index and team type to repo summary
add_diversity_dev <- function(commit_author_summary) {
  commit_author_summary$team_type <- NA
  commit_author_summary$shannon <- NA
  for (i in 1:nrow(commit_author_summary)) {
    f <- unlist(unname(commit_author_summary[i, "female"]))
    m <- unlist(unname(commit_author_summary[i, "male"]))
    ng <- unlist(unname(commit_author_summary[i, "no_gender"]))
    # Only classify repos with sufficient gender calls
    total <- m + f + ng
    if (ng / total > max_no_gender) next
    s <- shannon(c(f, m))
    commit_author_summary[i, "team_type"] <- classify(m, f, ng)
    commit_author_summary[i, "shannon"] <- s
  }
  commit_author_summary <- within(commit_author_summary, 
                                  team_type <- factor(team_type, levels=names(sort(table(team_type), decreasing=TRUE))))
  commit_author_summary
}
# Add diversity info to commit author summaries
commit_author_summary_main <- add_diversity_dev(commit_author_summary_main)
commit_author_summary_high_prof <- add_diversity_dev(commit_author_summary_high_prof)

# Add Shannon index to commit summary
add_diversity_commit <- function(commit_summary) {
  commit_summary$shannon <- NA
  for (i in 1:nrow(commit_summary)) {
    f <- unlist(unname(commit_summary[i, "female"]))
    m <- unlist(unname(commit_summary[i, "male"]))
    ng <- unlist(unname(commit_summary[i, "no_gender"]))
    total <- m + f + ng
    if (ng / total > 0.25) next
    s <- shannon(c(f, m))
    commit_summary[i, "shannon"] <- s
  }
  commit_summary
}
# Add diversity info to commit summaries
commit_summary_main <- add_diversity_commit(commit_summary_main)
commit_summary_high_prof <- add_diversity_commit(commit_summary_high_prof)

# Function to join diversity summaries for commit authors and commits
diversity_summary <- function(commit_author_summary, commit_summary) {
  # Join diversity of developers and commits
  commit_author_summary %>% 
    select(repo_name, shannon) %>% 
    rename(shannon_commit_authors = shannon) %>%
    left_join(commit_summary %>% 
                select(repo_name, shannon) %>% 
                rename(shannon_commits = shannon), by = "repo_name")
}

# Make diversity summaries
diversity_summary_main <- diversity_summary(commit_author_summary_main, commit_summary_main)
diversity_summary_high_prof <- diversity_summary(commit_author_summary_high_prof, commit_summary_high_prof)
```

## Analyze gender breakdown of paper authors by article

```{r paper_authors_summary}
# Function to get list of genders of a delimited author list
author_list_genders <- function(author_list, gender_table) {
  unname(
    sapply(
      sapply(
        author_list, function(x) trimws(unlist(strsplit(x, ";")))), 
      function(x) get_gender_full_name(x, gender_table)))
}

# Function to get gender/diversity info for a delimited author list
gender_stats_author_list <- function(author_list, gender_table) {
  genders <- author_list_genders(author_list, gender_table)
  rtrn <- NULL
  rtrn$female <- sum(genders == "female", na.rm = T)
  rtrn$male <- sum(genders == "male", na.rm = T)
  rtrn$na <- sum(is.na(genders))
  rtrn$first_author <- if(length(genders) > 1) genders[1] else NA
  rtrn$last_author <- if(length(genders) > 1) genders[length(genders)] else NA
  rtrn
}

# Function to summarize diversity info of author lists by repo
paper_authors_summary <- function(author_lists, gender_table) {
  rtrn <- data.frame(repo_name = character(),
                     title = character(),
                     female = integer(),
                     male = integer(),
                     no_gender = integer(),
                     team_type = character(),
                     first_author = character(),
                     last_author = character(),
                     shannon = numeric())
  for(i in 1:nrow(author_lists)) {
    repo_name <- author_lists[i, "repo_name"]
    title <- author_lists[i, "title"]
    author_list <- author_lists[i, "authors"]
    gender_stats <- gender_stats_author_list(author_list, gender_table)
    male <- gender_stats$male
    female <- gender_stats$female
    no_gender <- gender_stats$na
    team_type <- classify(male, female, no_gender)
    first_author <- gender_stats$first_author
    last_author <- gender_stats$last_author
    sd <- shannon(c(male, female))
    rtrn <- rbind(rtrn,
                  data.frame(repo_name = repo_name,
                             title = title,
                             female = female,
                             male = male,
                             no_gender = no_gender,
                             team_type = team_type,
                             first_author = first_author,
                             last_author = last_author,
                             shannon = sd))
  }
  rtrn
}

# Summarize author list diversity by repo
paper_authors_summary_main <- paper_authors_summary(author_lists_main, gender_main)
paper_authors_summary_high_prof <- paper_authors_summary(author_lists_high_prof, gender_high_prof)
```

## Summarize developers, commits, and paper authors by gender

```{r gender_summary_figure, fig.width = 10, fig.height = 8}
# Function to combine several diversity measurements into a tidy summary table
gender_summary_tidy <- function(developers, commits_no_null_login, paper_authors_summary, dataset_name) {
  paper_authors_summary_dedup_articles <- paper_authors_summary %>% 
    select(-repo_name) %>%
    unique()
  gender_summary_developers <- developers %>% 
    group_by(gender) %>% 
    dplyr::summarize(n = n()) %>% 
    filter(gender %in% c("female", "male")) %>% 
    mutate(total = sum(n), p = n / total) %>%
    mutate(stat = "Developers")
  gender_summary_commit_author <- commits_no_null_login %>%
    group_by(author_gender) %>% 
    dplyr::summarize(n = n()) %>% 
    rename(gender = author_gender) %>%
    filter(gender %in% c("female", "male")) %>% 
    mutate(total = sum(n), p = n / total) %>%
    mutate(stat = "Commits")
  gender_summary_first_author <- paper_authors_summary_dedup_articles %>%
    group_by(first_author) %>%
    dplyr::summarize(n = n()) %>%
    rename(gender = first_author) %>%
    filter(gender %in% c("female", "male")) %>% 
    mutate(total = sum(n), p = n / total) %>%
    mutate(stat = "First authors")
  gender_summary_last_author <- paper_authors_summary_dedup_articles %>%
    group_by(last_author) %>%
    dplyr::summarize(n = n()) %>%
    rename(gender = last_author) %>%
    filter(gender %in% c("female", "male")) %>% 
    mutate(total = sum(n), p = n / total) %>%
    mutate(stat = "Last authors")
  gender_summary_paper_authors <- data.frame(
    gender = c("female", "male"), 
    n = c(sum(paper_authors_summary_dedup_articles$female), sum(paper_authors_summary_dedup_articles$male))) %>% 
    mutate(total = sum(n), p = n / total) %>%
    mutate(stat = "Paper authors")
  
  rbind(gender_summary_commit_author, gender_summary_developers, gender_summary_paper_authors,
        gender_summary_first_author, gender_summary_last_author) %>%
    rename(Gender = gender) %>%
    mutate(Dataset = dataset_name)
}

# Make the diversity summaries
gender_summary_main <- gender_summary_tidy(developers_main, 
                                           commit_info_main$commits_no_null_login,
                                           paper_authors_summary_main, 
                                           "Main repos")
gender_summary_high_profile <- gender_summary_tidy(developers_high_prof, 
                                                   commit_info_high_prof$commits_no_null_login,
                                                   paper_authors_summary_high_prof, 
                                                   "High profile repos")
gender_summary_tidy <- rbind(gender_summary_main, gender_summary_high_profile)

# Reorder the factors
gender_summary_tidy <- within(gender_summary_tidy, stat <- factor(stat, levels=c("Developers", "Commits", "Paper authors", "First authors", "Last authors")))
# Add explicit zeros
for(t1 in unique(gender_summary_tidy$Gender)) {
  for(t2 in unique(gender_summary_tidy$stat)) {
    for(t3 in unique(gender_summary_tidy$Dataset)) {
      if(nrow(gender_summary_tidy %>% filter(Gender == t1 & stat == t2 & Dataset == t3)) == 0) {
        gender_summary_tidy <- 
          rbind(data.frame(gender_summary_tidy), 
                data.frame(Gender = t1, n = 0, 
                           total = sum(gender_summary_tidy %>% filter(stat == t2 & Dataset == t3) %>% select(n)), 
                           p = 0, stat = t2, Dataset = t3))
      }
    }
  }
}

# Make the plot
ggplot(gender_summary_tidy %>% filter(Gender == "female"), 
       aes(x = stat, y = p, fill = Dataset)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste(formatC(n, format="d", big.mark=","), 
                              " / ", 
                              formatC(total, format="d", big.mark=","), 
                              sep = "")), 
            position = position_dodge(width = 0.9), 
            vjust = -0.25,
            size = 5,
            fontface = "bold") +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 14, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 14),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16)) +
  ylab("Proportion of female contributors") +
  scale_fill_manual(values = c(color_high_prof, color_main)) +
  expand_limits(x = 5.7)
ggsave("gender_summary.pdf")
ggsave("gender_summary.png")
```

## Summarize number of repos by team composition

```{r plot_buckets_dev_team}
# Make bar plot of team types
bucket_plot_data_dev_team <- commit_author_summary_main %>% filter(!is.na(team_type))
ggplot(bucket_plot_data_dev_team, aes(x = team_type)) + 
  geom_bar(fill = "red3") +
  theme_bw() +
  ylab("Number of repos") +
  theme(axis.title.x = element_blank(),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12, angle = 45, hjust = 1)) +
  ggtitle(paste("Developer team composition (", nrow(bucket_plot_data_dev_team), " teams)", sep = ""))
```

```{r bubble_plot_team_composition, fig.width = 7, fig.height = 5}
# Make bubble plot of team types for developers and paper authors
make_team_comp_bubble_plot_data <- function(commit_author_summary, paper_authors_summary, dataset) {
  data <- left_join(commit_author_summary %>% 
                      select(repo_name, team_type) %>% 
                      rename(team_type_dev = team_type), 
                    paper_authors_summary %>% 
                      select(repo_name, team_type) %>% 
                      rename(team_type_aut = team_type), by = "repo_name") %>% 
    filter(!is.na(team_type_dev) & !is.na(team_type_aut)) %>% 
    select(team_type_dev, team_type_aut) %>% 
    group_by(team_type_dev, team_type_aut) %>% 
    dplyr::summarize(num_repos = n()) %>% 
    arrange(-num_repos)
  team_type_levels <- c("Solo male", "Majority male", "All male", "Solo female", "Majority female", "All female", "Equal")
  for(t1 in team_type_levels) {
    for(t2 in team_type_levels) {
      if(nrow(data %>% filter(team_type_dev == t1 & team_type_aut == t2)) == 0) {
        data <- rbind(data.frame(data), data.frame(team_type_dev = t1, team_type_aut = t2, num_repos = NA))
      }
    }
  }
  data <- within(data, team_type_dev <- factor(team_type_dev, levels = team_type_levels))
  data <- within(data, team_type_aut <- factor(team_type_aut, levels = team_type_levels))
  data %>% mutate(Dataset = dataset)
}

team_comp_bubble_plot_data <- rbind(make_team_comp_bubble_plot_data(commit_author_summary_main, paper_authors_summary_main, "Main repos"),
                                    make_team_comp_bubble_plot_data(commit_author_summary_high_prof, paper_authors_summary_high_prof, "High profile repos")) %>%
  filter(!is.na(num_repos))

most_repos <- max(team_comp_bubble_plot_data$num_repos, na.rm = T)
ggplot(team_comp_bubble_plot_data, aes(x = team_type_dev, y = team_type_aut, col = Dataset)) + 
  geom_point(aes(size = num_repos)) +
  geom_point(data = subset(team_comp_bubble_plot_data, Dataset == "High profile repos"), aes(size = num_repos)) +
  xlab("Commit authors") +
  ylab("Paper authors") +
  theme_bw() +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        plot.margin = margin(10, 10, 20, 10),
        legend.background = element_rect(color = "black", size = 0.3)) +
  labs(size = "Number of repos") +
  scale_color_manual(values=c(color_high_prof, color_main), labels = c("High profile repos", "Main repos")) +
  scale_size(breaks = c(1, seq(20, most_repos - most_repos %% 20, by = 20)))
ggsave("team_composition.pdf")
ggsave("team_composition.png")

# Print the number of teams included
sum(team_comp_bubble_plot_data$num_repos, na.rm = T)
```

## Plot diversity of developers and commits

```{r diversity_plot_dev_commit, fig.width = 10, fig.height = 8}
# Plot Shannon index of diversity within developer teams and commits
shannon_plt_data_devs_commits <- diversity_summary_main %>% 
  select(shannon_commit_authors, shannon_commits) %>% 
  filter(!is.na(shannon_commit_authors) & !is.na(shannon_commits)) %>% 
  group_by(shannon_commit_authors, shannon_commits) %>% 
  dplyr::summarize(num_repos = n()) %>% 
  arrange(-num_repos)
ggplot(shannon_plt_data_devs_commits, aes(x = shannon_commit_authors, y = shannon_commits, size = num_repos)) + 
  geom_point(color = "red3") +
  xlab("Shannon diversity index: unique commit authors") +
  ylab("Shannon diversity index: individual commits") +
  scale_x_continuous(limits = c(0, 0.7)) +
  scale_y_continuous(limits = c(0, 0.7)) +
  theme_bw() +
  theme(axis.title = element_text(size = 16),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.position = c(0.15, 0.85),
        legend.background = element_rect(color = "black", size = 0.3)) +
  labs(size = "Number of repos") +
  scale_size(breaks = c(1, unname(unlist(shannon_plt_data_devs_commits[1,3]))))

# Print the number of teams included
sum(shannon_plt_data_devs_commits$num_repos)
```

## Plot diversity of developers vs team size

```{r diversity_plot_dev_team_size, fig.width = 6, fig.height = 5}
# Plot Shannon index of diversity and developer team size
make_dev_team_size_plt_data <- function(commit_author_summary, dataset) {
  commit_author_summary %>% 
    mutate(team_size = male + female) %>% 
    select(team_size, shannon) %>% 
    filter(!is.na(shannon)) %>% 
    group_by(team_size, shannon) %>% 
    dplyr::summarize(num_repos = n()) %>% 
    arrange(-num_repos) %>%
    mutate(Dataset = dataset)
}

dev_team_size_plt_data <- rbind(make_dev_team_size_plt_data(commit_author_summary_main, "Main repos"),
                                make_dev_team_size_plt_data(commit_summary_high_prof, "High profile repos"))
most_repos <- unname(unlist(dev_team_size_plt_data[1,3]))
ggplot(dev_team_size_plt_data, aes(x = team_size, y = shannon, size = num_repos, col = Dataset)) + 
  geom_point(aes(size = num_repos)) +
  geom_point(data = subset(dev_team_size_plt_data, Dataset == "High profile repos"), aes(size = num_repos)) +
  xlab("Developer team size (female + male)") +
  ylab("Shannon diversity index: unique commit authors") +
  theme_bw() +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.background = element_rect(color = "black", size = 0.3)) +
  labs(size = "Number of repos") +
  scale_size(breaks = c(1, seq(40, most_repos - most_repos %% 40, by = 40))) +
  scale_x_log10(breaks = c(1, 10, 100, 1000, 10000))
ggsave("shannon.pdf")
ggsave("shannon.png")

# Print the number of teams in the figure
sum(dev_team_size_plt_data$num_repos)

# How many teams have nonzero Shannon index?
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "Main repos" & shannon != 0) %>% select(num_repos) %>% sum()
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "High profile repos" & shannon != 0) %>% select(num_repos) %>% sum()

# How many teams have zero Shannon index?
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "Main repos" & shannon == 0) %>% select(num_repos) %>% sum()
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "High profile repos" & shannon == 0) %>% select(num_repos) %>% sum()

# How many teams have Shannon index > 0.4?
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "Main repos" & shannon > 0.4) %>% select(num_repos) %>% sum()
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "High profile repos" & shannon > 0.4) %>% select(num_repos)

# How many teams have Shannon index <= 0.4?
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "Main repos" & shannon <= 0.4) %>% select(num_repos) %>% sum()
dev_team_size_plt_data %>% ungroup() %>% filter(Dataset == "High profile repos" & shannon <= 0.4) %>% select(num_repos) %>% sum()

```


## Push repo-level results to BigQuery tables

```{r push_to_bq}
# Function to push analysis to BigQuery
push_to_bq <- function(proj, commit_author_summary, commit_summary, paper_authors_summary) {
  upload_job_commit_authors <- insert_upload_job(project = proj, 
                                                 dataset = ds_analysis, 
                                                 table = table_gender_commit_authors, 
                                                 values = commit_author_summary,
                                                 create_disposition = "CREATE_IF_NEEDED", 
                                                 write_disposition = "WRITE_TRUNCATE")
  
  upload_job_commits <- insert_upload_job(project = proj, 
                                          dataset = ds_analysis, 
                                          table = table_gender_commits, 
                                          values = commit_summary,
                                          create_disposition = "CREATE_IF_NEEDED", 
                                          write_disposition = "WRITE_TRUNCATE")
  
  upload_job_paper_authors <- insert_upload_job(project = proj, 
                                                dataset = ds_analysis, 
                                                table = table_gender_paper_authors, 
                                                values = paper_authors_summary,
                                                create_disposition = "CREATE_IF_NEEDED", 
                                                write_disposition = "WRITE_TRUNCATE")
}

# Push data for main and high profile repos
push_to_bq(proj_main, commit_author_summary_main, commit_summary_main, paper_authors_summary_main)
push_to_bq(proj_high_prof, commit_author_summary_high_prof, commit_summary_high_prof, paper_authors_summary_high_prof)
```

## Session info

```{r session_info}
sessionInfo()
```


